Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-12 ms.tex
githole7

Figure X show the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for a black hole of mass $M_{\bullet} = 10^{XX}M_{\odot}$.  These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Figure ) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}]).  At early times ($\tau_{\star} \lesssim XXX$), stellar wind heating dominates, but at later times Compton heating dominates.   MSP heating is again found to be negligible at all black hole masses.  Epochs of thermally-unstable accretion are shown as a dashed line, indicating that Compton heating becomes important only during the phase of unstable accretion.

>>>>

Figure X show the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for a black hole of mass $M_{\bullet} = 10^{XX}M_{\odot}$.  These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}]).  At early times ($\tau_{\star} \lesssim XXX$), stellar wind heating dominates, but at later times Compton heating dominates.   MSP heating is again found to be negligible at all black hole masses.  Epochs of thermally-unstable accretion are shown as a dashed line, indicating that Compton heating becomes important only during the phase of unstable accretion.

### 2015-02-12 windheat.tex
githole7

The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on the generalization of Reimer's law given in \citet{SchroderCuntz:2005a} (their eq.~[4]) as
\begin{align}
  \dot{m}=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
\end{align}
where  $R_*$, $L_*$, $T_{\rm eff}$ and $g_*$ are the stellar radius,
luminosity, effective temperature, and surface gravity, respectively, the latter normalized to its solar value $g_{\odot}$.  The stellar radius and luminosity are estimated as (\citet{Kippenhahn&Weigert90}; Figs.~22.2) 22.3)
\begin{align}
L_*=
\begin{cases}
L_{\odot} (\Mstar/\Msun)^{3.2} & \Mstar > \Msun \\
L_{\odot} (\Mstar/\Msun)^{2.5} & \Mstar \le \Msun
\end{cases}
\end{align}
\begin{align}
R_*=
\begin{cases}
R_{\odot} (\Mstar/\Msun)^{0.57} & \Mstar > \Msun \\
R_{\odot} (\Mstar/\Msun)^{0.8} & \Mstar \le \Msun
\end{cases}
\end{align}
The wind velocity of main sequence winds $v_w (\Mstar, t)$ is assumed
to equal 430 km s$^{-1}$, corresponding to the escape speed of the
Sun; this produces an effective wind heating velocity for main
sequence winds alone of $XXX$, in agreement with the value of 150 km
s$^{-1}$ found by \citet{NaimanSoares-Furtado+:2013a} based on a more
sophisticated population synthesis treatment. {\bf BDM: true?
  correct}...{\bf AG: Wind velocity should depend on stellar
  properties like escape speed. But choose normalization so that we
  get the correct vw for the sun.}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{etaImp.pdf}
\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
  a stellar population of age $\tau_{\star}$.}
\end{figure}

>>>>

The MS wind mass loss rate $\dot{m}(\Mstar, t)$ is calculated based on the generalization of Reimer's law given in \citet{SchroderCuntz:2005a} (their eq.~[4]) as
\begin{align}
  \dot{m}=8 \times 10^{-14} \frac{L_* R_*}{\Mstar}
  \left(\frac{T_{\rm eff}}{\rm 4000 K}\right)^{3.5}
  \left(1+\frac{g_{\odot}}{4300 g_*}\right) \Msun \pyear,\
\end{align}
where  $R_*$, $L_*$, $T_{\rm eff}$ and $g_*$ are the stellar radius,
luminosity, effective temperature, and surface gravity, respectively, the latter normalized to its solar value $g_{\odot}$.  The stellar radius and luminosity are estimated as (\citet{Kippenhahn&Weigert90}; Figs.~22.2) 22.3)
\begin{align}
L_*=
\begin{cases}
L_{\odot} (\Mstar/\Msun)^{3.2} & \Mstar > \Msun \\
L_{\odot} (\Mstar/\Msun)^{2.5} & \Mstar \le \Msun
\end{cases}
\end{align}
\begin{align}
R_*=
\begin{cases}
R_{\odot} (\Mstar/\Msun)^{0.57} & \Mstar > \Msun \\
R_{\odot} (\Mstar/\Msun)^{0.8} & \Mstar \le \Msun
\end{cases}
\end{align}
The wind velocity of main sequence winds is assumed
to equal $v_w (\Mstar, t) = v_{w,\odot}(M_{\star}/M_{\odot})^{1/2}(R_{\star}/R_{\odot})^{-1/2}$, i.e.~scaling as the stellar escape velocity and normalized to the velocity of the solar wind $v_{w,\odot} = 430$ km s$^{-1}$; this produces an effective wind heating velocity for main
sequence winds alone of $\sim 100$ km s$^{-1}$ for $\tau_{\star} \sim t_{\rm h}$, close to the value found by \citet{NaimanSoares-Furtado+:2013a} for globular clusters based on a more
sophisticated population synthesis treatment.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{etaImp.pdf}
\caption{\label{fig:etaImp} The mass loss parameter, $\eta$ (eq.~[\ref{eq:q}]), resulting from stellar winds from
  a stellar population of age $\tau_{\star}$  {\bf BDM: combine with above figure into one}.}
\end{figure}
